---
title: "Tourism Data Analysis"
output:
  pdf_document: default
  html_document: default
date: "31 July 2019"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(Matrix)
library(hts)
library(readr)
library(tibble)
library(kableExtra)
library(reshape2)
library(ggpubr)
library(gridExtra)
```

<!-- ### Estimating the bias from the mean of the insample residuals -->
<!-- ```{r, echo=FALSE} -->
<!-- DF_Exp_1 <- read.csv("DF_Exp-1.csv")[,-1] -->

<!-- DF_Exp_1 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_Exp_1 -->

<!-- DF_Exp_1 %>%  -->
<!--   group_by(`F.method`, `R.method`, Forecast_Horizon) %>%  -->
<!--   summarise(MSE = mean(SquaredE)) -> Avg_MSE_Exp1 -->

<!-- Avg_MSE_tab1_Exp1 <- Avg_MSE_Exp1 %>%  -->
<!--   dcast(`R.method` ~ Forecast_Horizon + `F.method`, value.var = "MSE")  -->

<!-- colnames(Avg_MSE_tab1_Exp1) <- c("R.method", rep(c("Biased", "Unbiased"), 6)) -->

<!-- Avg_MSE_tab1_Exp1 %>%  -->
<!--   kable(format = "latex") %>%  -->
<!--   kableExtra::add_header_above(c(" " = 1, "h=1" = 2, "h=2" = 2, "h=3" = 2, "h=4" = 2, -->
<!--                                  "h=5" = 2, "h=6" = 2))  -->

<!-- ``` -->

### Bias adjusted forecasts are given as follows:

$$ y_t = 
  \begin{cases} 
   \exp{x_t}[1+\frac{\sigma_h^2}{2}] & \text{if } \lambda = 0 \\ \\
   (\lambda x_t + 1)^{1/\lambda}[1 + \frac{\sigma_h^2(1-\lambda)}{2(\lambda x_t + 1)^2}]       & \text{Otherwise}
  \end{cases}$$


### For BoxCox transformed data (Using the BoxCox function in the forecast package)

In this exercise I have used the `BoxCox.lambda()` function in forecast package to automatically find a proper transformation for each series.
```{r, echo=FALSE}
load("TourismData_BoxCoxTransBiasCorrection_UnivARIMA.RData")

DF %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_BoxCox_1

DF_BoxCox_1 %>% 
  group_by(`F-method`, `R-method`, Forecast_Horizon) %>% 
  summarise(MSE = mean(SquaredE)) -> Avg_MSE_BC_1

Avg_MSE_tab1_BC_1 <- Avg_MSE_BC_1 %>% 
  dcast(`R-method` ~ Forecast_Horizon + `F-method`, value.var = "MSE") 

colnames(Avg_MSE_tab1_BC_1) <- c("R-method", rep(c("Biased", "Unbiased"), 6))

Avg_MSE_tab1_BC_1 %>% 
  kable(format = "latex") %>% 
  kableExtra::add_header_above(c(" " = 1, "h=1" = 2, "h=2" = 2, "h=3" = 2, "h=4" = 2,
                                 "h=5" = 2, "h=6" = 2)) 

DF_BoxCox_1 %>% 
  mutate(Forecast_Horizon = recode(Forecast_Horizon, "1" = "h=1",  "2" = "h=2",
                                    "3" = "h=3",  "4" = "h=4",  "5" = "h=5",  
                                   "6" = "h=6")) %>%
  filter(`R-method` == "Base") %>% 
  group_by(`F-method`, `R-method`, Forecast_Horizon, Replication) %>% 
  summarise(MSE = mean(SquaredE)) %>% 
  spread(key = `F-method`, value = MSE) %>% 
  mutate("Bias-Unbias" = `ARIMA_bias` - `ARIMA_unbias`) %>% 
  ggplot(aes(x = Replication, y = `Bias-Unbias`)) + geom_point() + 
  facet_wrap(~Forecast_Horizon, scales = "free_y") +
  ylab("MSE (bias - unbias)") + 
  ggtitle("MSE Difference between Biased-base and Unbiased-base")

```

The above graph shows the difference between the MSE of `Base-biased forecasts` and `Base-unbiased forecasts`. As we can see, this difference is very large for some of the replications which courses the large average MSE in unbiased-base forecasts shown in the table 1.  

However an important thing to notice here is that although the unbiased base forecasts are terrible, MinT has adjusted these through the reconciliation. In fact the MinT reconciled unbiased forecasts are even better than the MinT reconciled biased forecasts. 


We have also noticed that the based-bias adjusted forecasts are going worst for only one variable which is `Adelaide Hills`. If we visualise this time series we get, 

```{r}
AllTS %>% 
  dplyr::select(`Adelaide Hills`) %>% 
  ts(start = c(1998, 1), frequency = 12) %>% 
  autoplot()
```


We can see this variable has an anomalous observation on Dec-2002 which might be an outlier. 

```{r}
AllTS %>% 
  dplyr::select(`Adelaide Hills`) %>% 
  slice(3:102) %>% 
  as.ts() %>% 
  BoxCox.lambda() -> lambda
  

```

If we do Box-Cox transformation for this series we get  $\lambda = `r lambda`$. The transformed series with this $\lambda$ looks like

```{r}
AllTS %>% 
  dplyr::select(`Adelaide Hills`) %>% 
  slice(3:102) %>% 
  ts(start = c(1998, 1), frequency = 12) %>% 
  BoxCox(lambda = lambda) %>% 
  autoplot()

```


```{r echo=FALSE}
TS <- AllTS %>% 
  dplyr::select(`Adelaide Hills`) %>% 
  slice(3:102) %>% 
  ts(start = c(1998, 1), frequency = 12)
```


```{r echo=FALSE}
# TS %>% 
#   auto.arima(lambda = "auto") %>% 
#   forecast(h=6, biasadj = FALSE) %>% 
#   autoplot() + 
#   ggtitle("Biased forecasts")
# 
# TS %>% 
#   auto.arima(lambda = "auto") %>% 
#   forecast(h=6, biasadj = TRUE) %>% 
#   autoplot() + 
#   ggtitle("Bias-adjusted forecasts")

```


I have replaced the anomalous observation in this series with the average of December for predecessive and successive years of 2002. Then I have refitted the models for automatically chosen Box-Cox transformed data. Back-transformed and back-transformed bias-adjusted forecasts were then obtained. The results are as follows. 

```{r echo=FALSE}
load("TourismData_BoxCoxTransBiasCorrectionM1_UnivARIMA_AnomalyAdj.RData")

DF %>% 
  mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_BoxCox_2

DF_BoxCox_2 %>% 
  group_by(`F-method`, `R-method`, Forecast_Horizon) %>% 
  summarise(MSE = round(mean(SquaredE)/1e3, digits = 2)) -> Avg_MSE_BC_2

Avg_MSE_tab1_BC_2 <- Avg_MSE_BC_2 %>% 
  dcast(`R-method` ~ Forecast_Horizon + `F-method`, value.var = "MSE") 

colnames(Avg_MSE_tab1_BC_2) <- c("R-method", rep(c("Biased", "Unbiased"), 6))

Avg_MSE_tab1_BC_2 %>% 
  kable(format = "latex") %>% 
  kableExtra::add_header_above(c(" " = 1, "h=1" = 2, "h=2" = 2, "h=3" = 2, "h=4" = 2,
                                 "h=5" = 2, "h=6" = 2)) 

```


These results also shows that, even though the bias-adjusted based forecasts are worst than that of biased base forecasts, the MinT reconciliation is outperforming.

```{r echo=FALSE}
Avg_MSE_BC_2 %>% filter(`F-method` == "ARIMA_bias", `R-method` == "Base") %>% 
  slice() %>% 
  ungroup() %>% 
  dplyr::select(MSE) %>% 
  as_vector() -> ARIMA_bias_Base

Avg_MSE_BC_2 %>% 
   spread(key = `F-method`, value = MSE) %>% 
   mutate(Bias_SS.MSE = round((1-(ARIMA_bias/ARIMA_bias_Base))*100, digits = 2), 
          Unbias_SS.MSE = round((1-(ARIMA_unbias/ARIMA_bias_Base))*100, digits = 2)) -> Avg_MSE_BC_2_SS

Avg_MSE_BC_2_SS %>% 
  gather(key = "F-method", value = SS_MSE, Bias_SS.MSE, Unbias_SS.MSE) %>% 
  mutate(`F-method` = recode(`F-method`, "Bias_SS.MSE" = "Bias", "Unbias_SS.MSE" = "Unbias")) %>%
  ungroup() %>% 
  rename("Forecasting method" = "F-method") %>% 
  mutate(`R-method` = factor(`R-method`, levels = c("Base", "MinT(Shrink)", "WLS", "OLS"))) %>% 
  filter(`R-method` %in% c("Base", "MinT(Shrink)", "WLS", "OLS" )) %>%
  ggplot(aes(x = Forecast_Horizon, y = SS_MSE, 
             color = `Forecasting method`, shape = `Forecasting method`)) + 
  theme(legend.position="bottom") +
  facet_wrap(~ `R-method`, scales = "free_y") +
  geom_point(size = 3) + 
  scale_shape_manual(values = 15:16) +
  scale_color_manual(values = c("Red", "#33CC33")) + 
  ylab("Skill Score (MSE) %") + 
  xlab("h")



```

```{r echo=FALSE}

DF_MSE <- DF %>% 
  mutate(SquaredE = (`Actual` - `Forecasts`)^2) %>% 
  group_by(`F-method`, `R-method`, Replication, Forecast_Horizon) %>% 
  summarise(MSE = mean(SquaredE)) %>% 
  mutate(Forecast_Horizon = recode(Forecast_Horizon, "1" = "h=1", "2" = "h=2", "3"= "h=3", "4" = "h=4", "5" = "h=5", "6" = "h=6"))


DF_MSE %>% 
  filter(`F-method`=="ARIMA_unbias", `R-method`%in% c("Base", "OLS", "MinT(Shrink)", "WLS")) %>% 
  spread(key = `R-method`, value = MSE) %>% 
  mutate("Base-OLS" = Base - OLS,
         "Base-MinT" = Base - `MinT(Shrink)`,
         "Base-WLS" = Base - WLS) %>% 
  dplyr::select(Replication, Forecast_Horizon, `Base-OLS`, `Base-MinT`, `Base-WLS`) %>%
  rename("OLS" = "Base-OLS", "MinT" = "Base-MinT", "WLS" = "Base-WLS") %>% 
  gather(`OLS`, `WLS`, `MinT`,  key = Method, value = MSE) %>% 
  mutate(Method = factor(Method, levels = c("OLS", "MinT", "WLS"))) %>% 
  ggplot(aes(x = Method, y = MSE)) + 
  geom_boxplot() + 
  facet_wrap(~`Forecast_Horizon`, scales = "free_y") + 
  ylab("MSE") + xlab("Reconciliation Method")

```


### For Log transformed data 

In this exercise I have used only the log transformation. As we can see from the results, the bias adjusted forecasts are outperforming biased forecasts as we would expect. 
```{r, echo=FALSE}
load("TourismData_LogTransBiasCorrectionM1_UnivARIMA.RData")

DF -> DF_Log

DF_Log %>% 
  mutate(SquaredE = (`Actual` - `Forecasts`)^2) %>% 
  group_by(`F-method`, `R-method`, Forecast_Horizon) %>% 
  summarise(MSE = mean(SquaredE)/1e3) -> Avg_MSE_Log

Avg_MSE_tab1_Log <- Avg_MSE_Log %>% 
  dcast(`R-method` ~ Forecast_Horizon + `F-method`, value.var = "MSE") 

colnames(Avg_MSE_tab1_Log) <- c("R-method", rep(c("Biased", "Unbiased"), 6))

Avg_MSE_tab1_Log %>% 
  kable(format = "latex") %>% 
  kableExtra::add_header_above(c(" " = 1, "h=1" = 2, "h=2" = 2, "h=3" = 2, "h=4" = 2,
                                 "h=5" = 2, "h=6" = 2)) 

```

```{r}

DF_log_MSE <- DF_Log %>% 
  mutate(SquaredE = (`Actual` - `Forecasts`)^2) %>% 
  group_by(`F-method`, `R-method`, Replication, Forecast_Horizon) %>% 
  summarise(MSE = mean(SquaredE)) %>% 
  mutate(Forecast_Horizon = recode(Forecast_Horizon, "1" = "h=1", "2" = "h=2", "3"= "h=3", "4" = "h=4", "5" = "h=5", "6" = "h=6"))


DF_log_MSE %>% 
  filter(`F-method`=="ARIMA_unbias", `R-method`%in% c("Base", "OLS", "MinT(Shrink)", "WLS"), Forecast_Horizon == "h=1") %>% 
  spread(key = `R-method`, value = MSE) %>% 
  mutate("Base-OLS" = Base - OLS,
         "Base-MinT" = Base - `MinT(Shrink)`,
         "Base-WLS" = Base - WLS) %>% 
  dplyr::select(Replication, `Base-OLS`, `Base-MinT`, `Base-WLS`) %>%
  rename("OLS" = "Base-OLS", "MinT" = "Base-MinT", "WLS" = "Base-WLS") %>% 
  gather(`OLS`, `WLS`, `MinT`,  key = Method, value = MSE) %>% 
  mutate(Method = factor(Method, levels = c("OLS", "MinT", "WLS"))) %>% 
  ggplot(aes(x = Method, y = MSE)) + 
  geom_boxplot() + 
  ylab("MSE") + xlab("Reconciliation Method")

  ```


